### 2017-06-15 manuscript/Appendix1.Rmd
updates calibration info to deal with scling factors

Using the RED and NIR reflectance values, we calculate the normalized difference vegetation index (NDVI) for each plot based on both AVHRR- and MODIS-based wavelengths.
We calculated NDVI as:

\begin{align}
\text{NDVI}_{\text{AVHRR}} &= \frac{b_3\delta_{1(\text{AVHRR})} - b_1\delta_{2(\text{AVHRR})}}{b_3\delta_{1(\text{AVHRR})} + b_1\delta_{2(\text{AVHRR})}} \\[10pt]
\text{NDVI}_{\text{MODIS}} &= \frac{b_4\delta_{1(\text{MODIS})} - b_2\delta_{2(\text{MODIS})}}{b_4\delta_{1(\text{MODIS})} + b_2\delta_{2(\text{MODIS})}}
\end{align}

\noindent{} where $b_x$ refers to band *x* (*x* = 1,2,3,4) in Table A1-1 and $\delta$s are scaling factors unique to each band.
The values for the scaling factors come from \textcolor{red}{(PETER?)} and are as follows: $\delta_{1(AVHRR)} = 0.77$, $\delta_{2(AVHRR)} = 1$, $\delta_{1(MODIS)} = 0.95$, $\delta_{2(MODIS)} = 0.96$.

>>>>

Using the RED and NIR reflectance values, we calculate the normalized difference vegetation index (NDVI) for each plot based on both AVHRR- and MODIS-based wavelengths.
We calculated NDVI as:
\vspace{-2em}
\begin{align}
\text{NDVI}_{\text{AVHRR}} &= \frac{b_3 - b_1}{b_3 + b_1} \\[10pt]
\text{NDVI}_{\text{MODIS}} &= \frac{b_4 - b_2}{b_4 + b_2}
\end{align}

\noindent{} where $b_x$ refers to band *x* (*x* = 1,2,3,4) in Table A1-1.

### 2017-06-15 manuscript/usses_water_ms.Rmd
updates calibration info to deal with scling factors

\begin{figure}[!ht]
  \centering
      \includegraphics[width=5in]{../figures/nmds_comp_combined.png}
  \caption{Nonmetric multidimensional scaling scores representing plant communities in each plot, colored by treatment. (A) NMDS results using basal cover data; (B) NMDS results using individual density data. 2011 is a pre-treatment year.}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=5in]{../figures/rank_clocks_cover.png}
  \caption{Rank clocks of average species' basal cover by treatment. (A) All species. (B) Dominant species. Cover is log-transformed to improve visualization of species with low cover.}
\end{figure}

>>>>

\begin{figure}[!ht]
  \centering
      \includegraphics[width=5in]{../figures/sppcomp_bray_all.png}
  \caption{Nonmetric multidimensional scaling scores representing plant communities in each plot, colored by treatment.}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=5in]{../figures/rank_clocks_scaled_abundance.png}
  \caption{Rank clocks of average species' scaled abundance by treatment. (A) All species. (B) Dominant species.}
\end{figure}
